Staged Abstract Interpreter

### 2018-01-05 paper.tex
outline

For example, k-CFA (k > 0) is a naturally global program analysis, because 
it need the last k calling contexts. But can we analyze programs (or libraries) separately 
which generate the specialized analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

For another example, programs are data for an abstract interpreter, if we have $n$ programs, then there 
are $n$ stages. Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.

@@

\section{Staged Abstracting Abstract Machine}

>>>>

For example, k-CFA (k > 0) is naturally a kind of whole program analysis, because 
it need the last k calling contexts. But can we analyze programs (or libraries) separately 
which generate the specialized analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

Another perspective, programs are data for an abstract interpreter, if we have $n$ programs, then there 
are $n$ stages. Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.

@@

\section{Staged Abstract Interpreter}
